Preliminary Experiment

### 2018-03-16 experiment_1/experiment_1.tex
fix typo

\item The third row displays the \% of simulations that resulted in ``extreme" market shares. Extreme market shares are defined as being simulations were one of the principals (either principal 1 or 2) ended up with 90\% or more of the market.
\end{enumerate}
\includepdf[pages={-}]{agents_table}
Comments: Almost everything is just a 50-50 split!
\begin{enumerate}
\item Almost all of the same algorithms pitted against each other ended with getting a 50/50 market share. This seems to be a good sanity check.
\item Strange things: focus on TS vs DEG (Heavy Tail). DEG wins for HM and HMR, but TS wins for SM. This seems weird? TS also seems to lose on HMR with Uniform prior.
\item Why does DynamicGreedy do so well on the HeavyTail prior? Does this make sense?
\end{enumerate}

>>>>

\item The third row displays the \% of simulations that resulted in ``extreme" market shares. Extreme market shares are defined as being simulations were one of the principals (either principal 1 or 2) ended up with 90\% or more of the market.
\end{enumerate}
\includepdf[pages={-}]{agents_table}
Comments: Almost everything is just a 50-50 split!
\begin{enumerate}
\item Almost all of the same algorithms pitted against each other ended with getting a 50/50 market share. This seems to be a good sanity check.
\item Things that stand out: DynamicGreedy does surprisingly well on the Heavy Tail prior. DG seems to beat both DEG and TS with the Heavy Tail prior. DEG also beats TS in the heavy tail prior, though TS seems to beat DG when the agent response function is SoftMax. Does this make sense?
\item Almost everything in both Uniform and Needle In Haystack - high ends up more or less being a tie.
\end{enumerate}

### 2018-03-16 preliminary/preliminary_report.tex
fix typo

$N = 200$ simulations were run. \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Needle-in-haystack
\begin{enumerate}
\item High (with three arms) - 2 arms with mean 0.50, 1 arm with mean 0.7 (+ 0.2)
\item High (with ten arms) - 9 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\item Medium-High (with ten arms) - 8 arms with mean 0.50, 1 arm with 0.60, 1 arm 0.80
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon = 0.05$
\item Non-Bayesian $\epsilon$-greedy - the greedy decision was made based on empirical mean. When there were zero observations, assumed that the empirical mean was 0 (this seems questionable), $\epsilon = 0.05$
\item UCB1 (with constant $1$)
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
	\For{Each experiment $i$}
		\State Use $p$ as the true distribution of the arms
		\State Generate realizations for each arm and round $t$ and instantiate bandit instance
		\For{Each algorithm $alg$}
			\State Run simulation for $T$ periods
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}

>>>>

$N = 200$ simulations were run. \\
\textbf{The Bandit priors that were considered}:
\begin{itemize}
\item Needle-in-haystack
\begin{enumerate}
\item High (with three arms) - 2 arms with mean 0.50, 1 arm with mean 0.7 (+ 0.2)
\item High (with ten arms) - 19 arms with mean 0.50, 1 arm with mean 0.70 (+ 0.20)
\item Medium-High (with ten arms) - 18 arms with mean 0.50, 1 arm with 0.60, 1 arm 0.80
\end{enumerate}
\end{itemize}
\textbf{Algorithms considered}:
\begin{enumerate}
\item ThompsonSampling with priors of $Beta(1, 1)$ for every arm.
\item DynamicGreedy with priors of $Beta(1, 1)$ for every arm
\item Bayesian Dynamic $\epsilon$-greedy with priors of $Beta(1, 1)$ for every arm and $\epsilon = 0.05$
\item Non-Bayesian $\epsilon$-greedy - the greedy decision was made based on empirical mean. When there were zero observations, assumed that the empirical mean was 0 (this seems questionable), $\epsilon = 0.05$
\item UCB1 (with constant $1$)
\end{enumerate}
\pagebreak
\textbf{Simulation Procedure}
\begin{algorithm}
\begin{algorithmic}[1]
\For{Each prior $p$}
	\For{Each experiment $i$}
		\State Use $p$ as the true distribution of the arms
		\State Generate realizations for each arm and round $t$ and instantiate bandit instance
		\For{Each algorithm $alg$}
			\State Run simulation for $T$ periods
		\EndFor
	\EndFor
\EndFor
\end{algorithmic}
\end{algorithm}
